Pulmonary acini exhibit complex changes during postnatal rat lung development

### 2021-04-09 manuscript.tex
Correct metadata [ci skip]
This build is based on
https://github.com/habi/acinar-analysis-manuscript/commit/457b81bb713828ba723145280d0ee7c4a8b18609.

This commit was created by the following CI build and job:
https://github.com/habi/acinar-analysis-manuscript/commit/457b81bb713828ba723145280d0ee7c4a8b18609/checks
https://github.com/habi/acinar-analysis-manuscript/runs/732396339

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/5e778036e316c47b8bac4ce50086b191a7e3707a/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/5e778036e316c47b8bac4ce50086b191a7e3707a}{habi/acinar-analysis-manuscript@5e77803}
on April 8, 2021.

@@

\begin{itemize}
\item
  \textbf{David Haberthür}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187}
  · \href{mailto:haberthuer@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(5e77803)}{haberthuer@ana.unibe.ch}
  · \includegraphics{images/github.svg}
  \href{https://github.com/habi}{habi}
  · \includegraphics{images/twitter.svg}
  \href{https://twitter.com/habi}{habi}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Eveline Yao}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Sébastien F. Barré}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Tiziana P. Cremona}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-0061-9578}{0000-0003-0061-9578}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Stefan A. Tschanz}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3880-4437}{0000-0003-3880-4437}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Johannes C. Schittny}✉
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-4025-3961}{0000-0003-4025-3961}
  · \href{mailto:schittny@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(5e77803)}{schittny@ana.unibe.ch}
  Institute of Anatomy, University of Bern, Switzerland
\end{itemize}

>>>>

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/457b81bb713828ba723145280d0ee7c4a8b18609/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/457b81bb713828ba723145280d0ee7c4a8b18609}{habi/acinar-analysis-manuscript@457b81b}
on April 9, 2021.

@@

\begin{itemize}
\item
  \textbf{David Haberthür}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187}
  · \href{mailto:haberthuer@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(457b81b)}{haberthuer@ana.unibe.ch}
  · \includegraphics{images/github.svg}
  \href{https://github.com/habi}{habi}
  · \includegraphics{images/twitter.svg}
  \href{https://twitter.com/habi}{habi}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Eveline Yao}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Sébastien F. Barré}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Tiziana P. Cremona}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-0061-9578}{0000-0003-0061-9578}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Stefan A. Tschanz}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3880-4437}{0000-0003-3880-4437}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Johannes C. Schittny}✉
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-4025-3961}{0000-0003-4025-3961}
  · \href{mailto:schittny@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(457b81b)}{schittny@ana.unibe.ch}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\end{itemize}
